\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-11 projects/project_5/molecular_dynamics/article/article.tex
added potential strength plot

    \subsection{Sampling quantities}
    \label{sub:sampling_quantities}

@@

\begin{thebibliography}{9}
\bibitem{thermoprotein}
    Cooper, A. (1976). Thermodynamic fluctuations in protein molecules. Proceedings of the National Academy of Sciences, 73, 2740-2741. Retrieved December 9, 2015, from \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{equipar} 
    Equipartition Theorem. (2015, November 21). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Equipartition_theorem}
\bibitem{folding}
    Levitt, M., \& Warshel, A. (1975). Computer simulation of protein folding. Nature, 253, 694-698. Retrieved December 7, 2015, from \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{min_image}
    Periodic boundary conditions. (2015, November 13). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions}
\bibitem{liquid_argon}
    Rahman, A. (1964). Correlations in the Motion of Atoms in Liquid Argon. Phys. Rev. Physical Review, 126(2A). Retrieved December 7, 2015, from \url{http://journals.aps.org/pr/pdf/10.1103/PhysRev.136.A405}
\bibitem{virial} 
    Virial Theorem. (2015, October 7). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Virial_theorem}
\end{thebibliography}
\end{document}

>>>>

    \subsubsection{Derivation}
    \label{ssub:derivation}

    The Velocity Verlet algorithm can be derived using Taylor expansion and
    this derivation follows closely that of \cite{velo-ver}. We start with
    $\vec{r}(t + \Delta t)$ and write this as a Taylor expansion:
    \begin{align*}
        \vec{r}(t + \Delta t) &= \vec{r}(t) + \Delta t \dot{\vec{r}}(t) +
        \frac{\Delta t^2}{2}\ddot{\vec{r}}(t) + \mathcal{O}(\Delta t^3).
    \intertext{We can rewrite this using that $\dot{\vec{v}}(t) = \vec{F}(\vec{r}(t)) / m$
    and that $\ddot{\vec{r}} = \vec{F}(\vec{r}(t)) / m$.}
        \vec{r}(t + \Delta t) &= \vec{r}(t) + \Delta t \vec{v}(t) + \frac{\Delta t^2}{2} \frac{\vec{F}(\vec{r}(t))}{m}+ \mathcal{O}(\Delta t^3). \\ 
    \intertext{We now look at $\vec{v}(t + \Delta t)$ and its Taylor expansion:}
        \vec{v}(t + \Delta t) &= \vec{t} + \Delta t \dot{\vec{v}}(t) \frac{\Delta t^2}{2}\ddot{\vec{v}}(t) + \mathcal{O}(\Delta t^3). \\
    \intertext{In order to simplify this, we need an expression for $\ddot{\vec{v}}$. So we look at the Taylor expansion for $\dot{\vec{v}}(t + \Delta t)$:}
        \dot{\vec{v}}(t + \Delta t) &= \dot{\vec{v}}(t) + \Delta t
        \ddot{\vec{v}}(t) + \mathcal{O}(\Delta t^2). \\
    \intertext{This equation can be solved for $\Delta t^2 \ddot{\vec{v}} / 2$ and when plugged into the equation above yields}
        \vec{v}(t + \Delta t) &= \vec{v}(t) + \Delta t  \dot{\vec{v}}(t) + \frac{\Delta t}{2}\left( \dot{\vec{v}}(t + \Delta t) - \dot{\vec{v}}(t)\right) + \mathcal{O}(\Delta t^3).\\
    \intertext{One final rewrite, using the standard equations of motion gives}
    \vec{v}(t + \Delta t) &= \vec{v}(t) + \frac{\Delta t}{2m} \left( \vec{F}(\vec{r}(t + \Delta t)) + \vec{F}(\vec{r}(t))\right) + \mathcal{O}(\Delta t)^3.
    \end{align*}
    \subsection{Sampling quantities}
    \label{sub:sampling_quantities}

@@

\begin{thebibliography}{9}
\bibitem{thermoprotein}
    Cooper, A. (1976). Thermodynamic fluctuations in protein molecules. Proceedings of the National Academy of Sciences, 73, 2740-2741. Retrieved December 9, 2015, from \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{equipar} 
    Equipartition Theorem. (2015, November 21). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Equipartition_theorem}
\bibitem{folding}
    Levitt, M., \& Warshel, A. (1975). Computer simulation of protein folding. Nature, 253, 694-698. Retrieved December 7, 2015, from \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{min_image}
    Periodic boundary conditions. (2015, November 13). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions}
\bibitem{liquid_argon}
    Rahman, A. (1964). Correlations in the Motion of Atoms in Liquid Argon. Phys. Rev. Physical Review, 126(2A). Retrieved December 7, 2015, from \url{http://journals.aps.org/pr/pdf/10.1103/PhysRev.136.A405}
\bibitem{velo-ver}
    J'onsson, H. (n.d.). Classical Dynamics. Retrieved December 11, 2015, from
    \url{https://notendur.hi.is//~hj/EE4/Verlet.pdf}
\bibitem{virial} 
    Virial Theorem. (2015, October 7). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Virial_theorem}
\end{thebibliography}
\end{document}
